\section{Regional Climate and the General Circulation}
\subsection{The Atmosphere}
An important aspect of the Arctic climate is the connection to the atmospheric circulation through the large-scale circulation patterns known as the Hadley, Ferrel, and Polar cells. The Polar cell is coupled with the general circulation and lifts air masses from the surface to the upper troposphere, moving them toward the North Pole, where they subside, creating a high-pressure system (as seen in \autoref{fig:SeaLevelPressure_mean}) \citep{hartmann2016}. This creates a dry desert-like climate and easterly surface winds. This circulation is directly coupled to the strength of the sea level pressure difference between the Arctic high-pressure and the mid-latitudes, which can be measured using the Arctic Oscillation (AO) index, which in turn is directly linked to the North Atlantic Oscillation (NAO) \citep{serreze2014}. In \autoref{fig:SeaLevelPressure_mean_DJF} and \autoref{fig:SeaLevelPressure_mean_JJA} one can see that the AO index is positive during the winter, while weaker during the summer. This is because the AO index is directly linked to the meridional temperature gradient, through the polar cell, thus creating stronger AO during the winter. 

\subsection{The Ocean}
The Arctic Ocean is connected to the Atlantic Ocean through the Fram Strait but is otherwise almost disconnected from the worlds oceans. Thus, most oceanic water entering and exiting the Arctic Ocean passes through the Fram Strait (as seen in \autoref{fig:SeaSurfaceTemperature_annual}) \citep{serreze2014}. The incoming water is the Norwegian Current, which is a branch of the Gulf Stream and thus warm and saline. When this water reaches higher latitudes, it is much warmer than the atmosphere, leading to a large heat flux from the ocean to the atmosphere. Furthermore, the water becomes less saline as it mixes with freshwater from river discharge. As some water freezes, brine rejection leads to an increase in salinity and thus an increase in potential density, causing the water to sink. Interestingly, this creates an increase in temperature with depth for the initial hundred meters, which is the opposite of other oceans \citep{serreze2014}.

Thus, water that entered the Arctic Ocean through the Fram Strait leaves the Arctic Ocean through the Fram Strait, but as cold and less saline North Atlantic Deep Water (NADW). These processes are an important part of the Atlantic meridional overturning circulation. Additionally, large river discharge into the Arctic requires a compensating export of ocean water to maintain the water budget. Together with surface winds and density gradients, a southward transport of cold, icy Arctic surface water known as the East Greenland Current is formed. The flow is in geostrophic balance, which explains its proximity to the Greenland coast, and it continues southward as the Labrador Current \citep{serreze2014}

Furthermore, sea ice circulates clockwise in the Arctic Ocean due to Ekman transport driven by polar easterlies, which creates an anticyclonic sea surface circulation (Beaufort High) \citep{serreze2014}. This process results in the formation of layers of old sea ice along the Arctic Archipelago. However, as the sea-ice passes through the Fram Strait it is exported into the North Atlantic.
