\section{Climate Changes: Ongoing and Projected for the Future}
According to \citet{serreze2011}, the Arctic is warming at a faster rate than the rest of the world. Due to the increasing decline of sea ice during the summer months, the albedo of the region is decreasing, leading to greater absorption of solar radiation during the time when most solar radiation is available, and thus amplified heating. A study by \citet{rantanen2022} shows that during 1979--2021 the Arctic has warmed by more than four times the global average. Thus, the Arctic is experiencing a phenomenon called Arctic amplification, which is the enhanced warming of the Arctic compared to the rest of the world. According to \citet{IPCC2023}, the Arctic is projected to continue warming at a faster rate than the global average, with the warming affecting ecosystems and human communities in the region.
\newpage
Another important aspect of climate change in the Arctic is the thawing of permafrost \citep{serreze2014}. The thawing of permafrost is another positive feedback mechanism that can lead to further warming in the Arctic due to the release of greenhouse gases into the atmosphere, which can further enhance the greenhouse effect \citep{IPCC2023}. The thawing of permafrost can also lead to changes in the landscape, such as the formation of thermokarst (terrain collapse caused by thawing) and thus collapse of infrastructure built on this permafrost. Furthermore, rivers in the Arctic, such as the Mackenzie, Lena, Yenisey, and Ob, may change their flow patterns due to changes in the landscape, according to \citet{serreze2014}. This would have significant impacts on freshwater flow into the Arctic Ocean and sea-ice formation. These changes may completely alter the heat balance of the Arctic and prevent the formation of sea ice, or even cause the Arctic Ocean to freeze to the bottom during winter. Thus, a complete change in the heat balance and important ocean currents from the region may be expected \citep{hartmann2016}. As a consequence, the Arctic is estimated to be ice-free during the summer months by the year 2050 \citep{hartmann2016}. Communities dependent on sea ice for their livelihoods, such as Indigenous peoples, may therefore face even greater challenges as sea ice continues to decline \citep{IPCC2023}.